Luminance constancy under fixed geometry

### 2018-05-01 Draft4/draft4.tex
relative RMSE definition in words

Figure~\ref{fig:barGraphs} summarizes luminance constancy performance across the conditions, for both AMA and linear regression. 
We quantified overall performance in terms of overall relative root mean squared estimation error (relative RMSE) for the test set defined as:
\begin{align}
E_{\rm rel} = \sqrt{\left\langle\left(\frac{\rm{LRV_{Estimated}-LRV_{True}}}{\rm{LRV_{True}}}\right)^2\right\rangle}
\label{eq:relRMSe}
\end{align}
where the expectation is taken over all test stimuli at all LRVs.
The height of each bar gives the relative RMSE for each method and condition.
Note first that AMA improves upon linear regression for all conditions but the first, where performance for both methods is essentially perfect.
This is expected since AMA makes optimal use of the stimulus information under a wider range
of conditions than linear regression.
Moreover, the linear regression method we use as a baseline here
only has access to cone isomerizations at image locations corresponding to the target object, while AMA has access to isomerizations from the entire image patch.
Second, the fact that performance for Condition 2 is very poor tells us that that when there is substantial intensity variation in the illuminant, achieving luminance constancy
directly from the cone isomerizations is difficult.
Performance improves greatly when we consider the same condition but when the cone isomerizations are contrast normalized. 
Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
Note, however, that Condition 2 does not include variation in the background surface reflectances.
Such reflectances vary scene to scene in natural viewing.
The results for Condition 3 show performance when we add such variation into the training and test sets.
The error here represents the overall level of luminance constancy that our methods achieve for the
most realistic condition that we tested.

>>>>

Figure~\ref{fig:barGraphs} summarizes luminance constancy performance across the conditions, for both AMA and linear regression. 
We quantified overall performance in terms of overall relative root mean squared estimation error (relative RMSE) for the test set. The relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV. The mean is taken over all stimuli in the test set.
%\begin{align}
%E_{\rm rel} = \sqrt{\left\langle\left(\frac{\rm{LRV_{Estimated}-LRV_{True}}}{\rm{LRV_{True}}}\right)^2\right\rangle}
%\label{eq:relRMSe}
%\end{align}
%where the expectation is taken over all test stimuli at all LRVs.
The height of each bar gives the relative RMSE for each method and condition.
Note first that AMA improves upon linear regression for all conditions but the first, where performance for both methods is essentially perfect.
This is expected since AMA makes optimal use of the stimulus information under a wider range
of conditions than linear regression.
Moreover, the linear regression method we use as a baseline here
only has access to cone isomerizations at image locations corresponding to the target object, while AMA has access to isomerizations from the entire image patch.
Second, the fact that performance for Condition 2 is very poor tells us that that when there is substantial intensity variation in the illuminant, achieving luminance constancy
directly from the cone isomerizations is difficult.
Performance improves greatly when we consider the same condition but when the cone isomerizations are contrast normalized. 
Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
Note, however, that Condition 2 does not include variation in the background surface reflectances.
Such reflectances vary scene to scene in natural viewing.
The results for Condition 3 show performance when we add such variation into the training and test sets.
The error here represents the overall level of luminance constancy that our methods achieve for the
most realistic condition that we tested.
